Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-01-28 draft_lm1.tex
update figure 3 and code to generate it
Sorry for that; fixes #11
updated discussion

Based on the what has been discussed so far, we can rewrite (\ref{eq:AR}) for 
each epidemic $j$ as
\begin{equation}
\label{eq:AR2}
 A_{j}=\frac{\sum Y_j}{S_{0j}}
\end{equation}
where $S_{0j}$ is the number of susceptibles before each epidemic $j$, which we
estimated as described above.

@@

Figure \ref{fig:rtseries}  shows the $R_t$ series, according to 
(\ref{eq:Rtestimate}). 
It can be seen that the inter-epidemic periods are characterized by $R_t$ being 
indistinguishable from 1.

@@

The authors hope that this evidence will motivate public health 
outhorities to invest in annual serological surveys, to determine the profile 
of susceptibility to each dengue virus as well as to estimate the 
underreporting factor of the notification system.
% We only support three levels of headings, please do not create a heading level below \subsubsection.
%\subsection*{Subsection 1}
%\section*{Discussion}
% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
LMC is grateful to Dr. Leonardo Bastos for useful discussions on the 
posterior inference for $R(t)$.
The authors are also grateful to Claudia T. 
Code\c{c}o for helpful discussions about the manuscript.

@@

As a side note, the Bayesian approach presented in this 
paper will give similar results to those of 
\cite{wilson} and \cite{wilson} for $Y_{t+1}$ and $Y_t >> 1$.
Under the flat  uniform prior for $\theta_t$, the Bayesian posterior 
credibility 
interval is nearly indistinguishable from the confidence interval proposed by 
\citet{clopper} for $Y_{t+1}, Y_t > 20$.
Note that the $Beta(1, 1)$ uniform prior for $\theta_t$ constitutes a poor 
prior 
choice mainly because the induced distribution for \rr is only well-defined for 
$b_0 > 2$.

@@

\bibliography{lm1}
\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{plots/concat_SI.png}
\end{center}
\caption{
{\bf Susceptibles and Infectious posterior curves.}  The curves were estimated 
only for the periods where $R_t> 1$.  The susceptible curves in the top panel 
reflect the prevalence of fraction of susceptibles to circulating strain(s) for 
each epidemic/outbreak. In the lower panel see the posterior distribution 
of infectious curves, represented by its Median and 95\% credible interval. 
Scatter plot shows the observed cases. Prevalences are scaled as fractions 
of the entire population.
}
\label{Fig:S0}
\end{figure}

>>>>

Based on what has been discussed so far, we can rewrite (\ref{eq:AR}) for 
each epidemic $j$ as
\begin{equation}
\label{eq:AR2}
 A_{j}=\frac{\sum Y_j}{S_{0j}}
\end{equation}
where $S_{0j}$ is the number of susceptibles before each epidemic $j$, which we
estimated before.

@@

Figure \ref{fig:rtseries}  shows the $R_t$ series, according to 
(\ref{eq:Rtestimate}). 
It can be seen that the inter-epidemic periods are characterized by $R_t$ being 
indistinguishable from 1. Due to the instrinsic variability of the \rr series, 
the exmination of its credible intervals is essential to identify periods 
of sustained transmission. The wider credible intervals for the interepidemic 
periods are due to the scarsity of cases. Our methodology to derive the 
probability distribution for \rr is an original contribution applicable to the 
analysis of any incidence time-series of  any transmissible disease.

@@

The authors hope that this evidence will motivate public health 
outhorities to invest in annual serological surveys, to determine the 
susceptibility profile to each dengue virus as well as to estimate the 
underreporting factor of the notification system.
% We only support three levels of headings, please do not create a heading level below \subsubsection.
%\subsection*{Subsection 1}
%\section*{Discussion}
% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
LMC is grateful to Dr. Leonardo Bastos for useful discussions on the 
posterior inference for $R(t)$.
The authors are also grateful to Claudia T. 
Code\c{c}o for helpful discussions about the manuscript.

@@

As a side note, the Bayesian approach presented in this 
paper will give similar results to those of 
\cite{wilson} and \cite{wilson} for $Y_{t+1}$ and $Y_t >> 1$.
Under the flat  uniform prior for $\theta_t$, the Bayesian posterior 
credibility 
interval is nearly indistinguishable from the confidence interval proposed by 
\cite{clopper} for $Y_{t+1}, Y_t > 20$.
Note that the $Beta(1, 1)$ uniform prior for $\theta_t$ constitutes a poor 
prior 
choice mainly because the induced distribution for \rr is only well-defined for 
$b_0 > 2$.

@@

\bibliography{lm1}
\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{plots/concat_SI.png}
\end{center}
\caption{
{\bf Susceptibles and Infectious posterior curves.}  The curves were estimated 
only for the periods where $R_t> 1$.  The susceptible curves in the top panel 
reflect the prevalence of fraction of susceptibles to circulating strain(s) for 
each epidemic/outbreak. In the lower panel see the posterior distribution 
of infectious curves, represented by its Median and 95\% credible interval. The 
credible intervals are very narrow, and can be hard to distiguish from the 
median line. 
Scatter plot shows the observed cases. Prevalences are scaled as fractions 
of the entire population.
}
\label{Fig:S0}
\end{figure}
